Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-07 article/article.tex
Commit 2024-06-07 14:14

An important aspect of the variability of solar radiation is its
interaction with the clouds. In general, clouds can attenuate a fraction
of solar irradiance, but under certain conditions, can lead to
enhancement of the global horizontal irradiance (GHI) reaching the
ground. This effect can locally increase the observed GHI to levels even
higher than the expected clear-sky irradiance \citep[ see references
therein]{Cordero2023, Vamvakas2020}.

>>>>

An important aspect of the variability of solar radiation is its
interaction with the clouds. In general, clouds can attenuate a fraction
of solar irradiance, but under certain conditions, can lead to
enhancement of the global horizontal irradiance (GHI) reaching the
ground. This effect can locally increase the observed GHI to levels even
higher than the expected clear-sky irradiance {[}see references
therein{]}.
